---
title: "Proposal"
name: Madison Buntrock 
due: 8:00 PM EST, Tuesday, January
output: html_document
---

1. Pick some data to work with
```{r}
library(carData)
data(Vocab)

```

2. Perform some kind of analysis, which may result in one or
more of:
(a) Numerical results
(b) A complex object (like a regression analysis)
(c) Graphical results (like a plot)
```{r}
library(ggplot2)
#Is education predictive of vocab scores? 

voc.regression <- lm(vocabulary ~ education, data = Vocab)
str(voc.regression)



ggplot(Vocab, aes(education, vocabulary))+ geom_point() + geom_smooth(method = "lm")+facet_wrap(~year)

ggplot(Vocab, aes(education, vocabulary))+ geom_histogram(stat = "identity")+facet_wrap(~year)






```
3. Report the analysis with appropriate documentation
```{r}

# r = .33, 33% of variance of vocab scores is explained by education. This is a moderate positive correlation between education level and vocabulary scores. When grouped by year this effect is consistent. 

```

4. Some aspect of the above (data/analysis/reporting) needs to be
“non-trivial,” i.e., something we have not explicitly covered in
class. Examples include:
• Data: especially messy/big/complex data Example: analyze a complex public
data set, with code that would be
helpful to other people in wrangling
this data set to work with on their own
• Programming-dependent analysis: doing something that
would be difficult/infeasible/impossible/annoying with a
simple “point-and-click” program interface Example: a simulation-based analysis
requiring loops/iteration • Results: tricky visualization, novel way of reporting results
Example: a cool new way to visually
• Code: providing useful new function that would be of inter- represent/explore data in your field
est to other people Example: a convenience function
that people in your lab could use in
analyzing data that they commonly
work with
```{r}
quartile.sum.vocab <- for(this.group in c("1974", "1976", "1978", "1982", "1984", "1987", "1988", "1989", "1990", "1991", "1993", "1994", "1996", "1998", "2000", "2004",  "2006", "2008", "2010", "2012", "2014", "2016")) {
  print(summary(Vocab[Vocab$year == this.group, ])) 
}


```


5. Post results and replicable code via GitHub (preferred), or
email a complete zipped repository to me. This will be described
fully in class. The requirement means that your code
should compile/run/complete fully. If it does, and it does what
you said in your proposal, then the project will be complete.
You will be able to verify that it works ahead of time, so there
should be no uncertainty in whether the project “passes” or not.
The due date for the project is  


